Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-21 paper.tex
Wilder's comments
Closes #182

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10,11]{Jared G. Galloway}
\author[12,13]{Ariella L. Gladstein}
\author[14]{Gregor Gorjanc}
\author[15]{Bing Guo}
\author[7]{Ben Jeffery}
\author[16]{Warren W. Kretzschmar}
\author[17]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[18]{Michael Matschiner}
\author[17]{Dominic Nelson}
\author[19]{Nathaniel S. Pope}
\author[20]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[21]{Kumar Saunack}
\author[22]{Thibaut Sellinger}
\author[23]{Kevin Thornton}
\author[9]{Hugo van Kemenade}
\author[7]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[16,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[24,$\dagger$]{Jere Koskela}
\author[10,25,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo, Hugo
\affil[9]{No affiliation}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology,
    University of Oregon}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research
Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[13]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of
Medicine, Baltimore, MD}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute}
% Simon, Dom, Ivan
\affil[17]{Department of Human Genetics, McGill University}
% Michael
\affil[18]{Natural History Museum, University of Oslo}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California Irvine}
% Jere
\affil[24]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[25]{Department of Mathematics, University of Oregon}

@@

The software ecosystem built around \tskit\ is stable and mature;
simulators such as
\fwdpy~\citep{thornton2014cpp},
\SLiM~\citep{haller2019slim},
\stdpopsim~\citep{adrion2020community},
\texttt{Geonomics}~\citep{de2021geonomics}
and
\texttt{GSpace}~\citep{virgoulay2021gspace},
and inference methods such as
\texttt{tsinfer}~\citep{kelleher2019inferring},
\texttt{tsdate}~\citep{,wohns2021unified}
and \texttt{Relate}~\citep{speidel2019method}
use either the Python or C
APIs to support outputting results in tree sequence format.
Tree sequences are stored in an efficient binary file format, and
are fully portable across operating systems and processor
architectures. The \tskit\ library ensures interoperability
between programs by having strict definitions of how the
information in each of the tables is interpreted, and
stringent checks for the internal consistency of the data model.

@@

% We can simulate so much more now
The 1.0 release of \msprime\ marks a major increase in the
breadth of available features and the
potential biological realism of simulations.
These abilities will allow researchers to perform more robust power analyses,
more reliably test new methods,
carry out more reliable inferences,
and more throughly explore the properties of theoretical models.
Despite this complexity and generality,
\msprime's performance is state-of-the-art
and all features are thoroughly tested and statistically validated.
These advances have only been possible thanks to a distributed,
collaborative model of software development,
and the work of many people.
% We hope the tool continues to be useful to many.

>>>>

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10,11]{Jared G. Galloway}
\author[12,13]{Ariella L. Gladstein}
\author[14]{Gregor Gorjanc}
\author[15]{Bing Guo}
\author[7]{Ben Jeffery}
\author[16]{Warren W. Kretzschmar}
\author[17]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[18]{Michael Matschiner}
\author[17]{Dominic Nelson}
\author[19]{Nathaniel S. Pope}
\author[20]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[21]{Kumar Saunack}
\author[22]{Thibaut Sellinger}
\author[23]{Kevin Thornton}
\author[9]{Hugo van Kemenade}
\author[7,24]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[16,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[25,$\dagger$]{Jere Koskela}
\author[10,26,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo, Hugo
\affil[9]{No affiliation}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology,
    University of Oregon}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research
Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[13]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of
Medicine, Baltimore, MD}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute}
% Simon, Dom, Ivan
\affil[17]{Department of Human Genetics, McGill University}
% Michael
\affil[18]{Natural History Museum, University of Oslo}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California Irvine}
% Wilder 2
\affil[24]{Broad Institute of MIT and Harvard}
% Jere
\affil[25]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[26]{Department of Mathematics, University of Oregon}

@@

The software ecosystem built around \tskit\ is stable, mature and
rapidly growing.
Simulators such as
\fwdpy~\citep{thornton2014cpp},
\SLiM~\citep{haller2019slim},
\stdpopsim~\citep{adrion2020community},
\texttt{Geonomics}~\citep{de2021geonomics}
and
\texttt{GSpace}~\citep{virgoulay2021gspace},
and inference methods such as
\texttt{tsinfer}~\citep{kelleher2019inferring},
\texttt{tsdate}~\citep{,wohns2021unified}
and \texttt{Relate}~\citep{speidel2019method}
use either the Python or C
APIs to support outputting results in tree sequence format.
Tree sequences are stored in an efficient binary file format, and
are fully portable across operating systems and processor
architectures. The \tskit\ library ensures interoperability
between programs by having strict definitions of how the
information in each of the tables is interpreted, and
stringent checks for the internal consistency of the data model.

@@

% We can simulate so much more now
The 1.0 release of \msprime\ marks a major increase in the
breadth of available features and the
potential biological realism of simulations.
These abilities will allow researchers to perform more robust power analyses,
more reliably test new methods,
carry out more reliable inferences,
and more thoroughly explore the properties of theoretical models.
Despite this complexity and generality,
\msprime's performance is state-of-the-art
and all features are extensively tested and statistically validated.
These advances have only been possible thanks to a distributed,
collaborative model of software development,
and the work of many people.
% We hope the tool continues to be useful to many.
